Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2019-04-06 GWLDCI.tex
some picures and edits in section 1 and 2 (paper 1)

Propagators are undirected, so $p = (i,j) = (j,i)$. In order to fix a convention, we write $p = (i,j)$ with  $i +1 < j$ relative to the first vertex.

We depict this data as a circle with marked points, called vertices. The vertices are labeled by $V$ (preserving the cyclic ordering). The arc between consecutive vertices are called edges. There are $k$ wavy lines in the interior of the diagram, depicting the proagators, with endpoints on the edges. A propagator, $p =(i,j)$ has one endpoint on the edge between the vertex labeled $i$ and $i+1$ and another endpoint on the edge defined by $j$ and $j+1$. The condition\note{which condition is this referring to; I think it is talking about one of the admissibility conditions, so maybe this is in the wrong place, alternately the condition might have gotten deleted at some point} on $i_r$ and $j_r$ means that the propagator does not go between adjacent edges. Let $\cP = \{p_r\}_{r=1}^k$ be the set of propagators. Then we write \bas W = (\cP, V) \;.\eas \sanote{picture}

@@

@@

@@

We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to [ref][find a good matroid reference].\note{Oxley is always my go to reference for matroids, but perhaps it has the wrong focus for you?}

@@

%\begin{thebibliography}{10}
%\bibliographystyle{plain}
%\bibliography{C:/Users/agarws1/Documents/GitHub/OldWLDPapers/Bibliography}

@@

>>>>

Propagators are undirected, so $p = (i,j) = (j,i)$. In order to fix a convention, we write $p = (i,j)$ with  $i +1 \leq j$ relative to the first vertex.

We depict this data as a circle with marked points, called vertices. The vertices are labeled by $V$ (preserving the cyclic ordering). The arc between consecutive vertices are called edges. There are $k$ wavy lines in the interior of the diagram, depicting the proagators, with endpoints on the edges. A propagator, $p =(i,j)$ has one endpoint on the edge between the vertex labeled $i$ and $i+1$ and another endpoint on the edge defined by $j$ and $j+1$. Then we write \bas W = (\cP, V) \;.\eas

@@

For instance, 
\bas W = (\cP, [8]) = \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawprop{1}{0}{4}{0}
	\drawprop{2}{0}{4}{-1}
\drawprop{5}{0}{8}{0}
		\end{scope}
	\end{tikzpicture}  \eas with $\cP = \{ (1,4), (2, 4), (5, 8)\}$ is a Wilson loop diagram.

@@

\begin{eg}
The Wilson loop diagram $W$ shown above is exact. There is a single non-supporting vertex in $W$, $F(\emptyset) = \{7\}$. The subdiagram $(\{(2, 4), (1, 4)\}, \{1, 2, 3, 4, 5, \})$ is an exact subdiagram of $W$. For $p = (5, 8)$ $F(p) = \{6, 7,8\}$. 
\end{eg}

@@

We first give a quick summary of the matroid terminology that we will need; it is not intended as a comprehensive introduction to matroids and the interested reader is referred to \cite{OxleyMatroidBook}

@@

%\bibliographystyle{plain}
%\bibliography{C:/Users/agarws1/Documents/GitHub/OldWLDPapers/Bibliography}

@@

\bibitem{OxleyMatroidBook}
James~G. Oxley.
\newblock {\em Matroid Theory}, volume~21 of {\em Oxford graduate texts in
  mathematics}.
\newblock Oxford University Press, New York, 2011.
